\myTitle

### 2023-11-28 body-text-of-paper.tex
moved extra figures to supplement directory, if those even end up being used. added new figure of simulations

SNP filtering resulted in 14,233 loci that were used for subsequent analysis.
Using the 160 empirical samples, ADMIXTURE results supported the identification of
3 genetic clusters (SUPPLEMENTAL FIGURE). Admixture $q$ values clearly grouped individuals
from each of the core populations into 3 clusters while the 40 individuals from the contact regions were
highly admixed (SUPPLEMENTAL FIGURE). The
$F_{ST}$ divergence from ADMIXTURE was:
$F_{ST} = 0.24$ for Pop1-Pop2,
$F_{ST} = 0.14$ for Pop1-Pop14 and
$F_{ST} = 0.13$ for Pop2-Pop14.

The simulated hybrid classes produce
the expected range of admixture with $F_1$ and $F_2$ individuals having mean $q=0.5$, with $F_2$ individuals having
more variation. Backcrossed individuals have higher ancestry associated with the backcrossed population with $q$
approximately $0.75$ ($BC_1$) and $0.875$ ($BC_2$) (Figure~\ref{fig:pig-sim-qs}).

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize ADMIXTURE estimates of $q$ for $K=3$ of the simulated hybrid classes
($F_1$, $F_2$, $BC_1$ and $BC_2$) from all two-population combinations of the invasive wild pig genotypes.
Rows and columns provide the population combinations of the hybrids and for backcrossed hybrids the rows
specify the backcrossed population. Plots where the rows and columns specify the same population depict the
$q$ values for simulated non-hybrid (or "Core") individuals from the population.}
\includegraphics[width=0.96\textwidth]{figures/simulated-pigs-Q-facet.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%

>>>>

SNP filtering resulted in 14,233 loci that were used for subsequent analysis.
Using the 160 empirical samples, ADMIXTURE results supported the identification of
3 genetic clusters (SUPPLEMENTAL FIGURE). Admixture $q$ values clearly grouped individuals
from each of the core populations into 3 clusters while the 40 individuals from the contact regions were
highly admixed (SUPPLEMENTAL FIGURE). The
$F_{ST}$ divergence from ADMIXTURE was:
$F_{ST} = 0.24$ for Pop1-Pop2,
$F_{ST} = 0.14$ for Pop1-Pop14 and
$F_{ST} = 0.13$ for Pop2-Pop14. The simulated hybrid classes produce
the expected range of admixture with $F_1$ and $F_2$ individuals having mean $q=0.5$, with $F_2$ individuals having
more variation. Backcrossed individuals have higher ancestry associated with the backcrossed population with $q$
approximately $0.75$ ($BC_1$) and $0.875$ ($BC_2$) (Figure~\ref{fig:pig-sim-qs}). MATT NEEDS TO AUGMENT AND 
REVISE THE RESULTS

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize MATT NEEDS TO ADD CAPTION.}
\includegraphics[width=0.96\textwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%
